\fancyhead[CE]{\fontsize{\thefontsize}{\thefontsize}\selectfont\Large Mr.\ \emph{Le Clerc}'s= Advice about}
\fancyhead[CO]{\fontsize{\thefontsize}{\thefontsize}\selectfont\Large the Use of \emph{Common-Places=}.}
\thispagestyle{doublerule}
\vspace*{0pt}
\setcounter{page}{1}
\renewcommand\thepage{\roman{page}}
\fancyhead[RO]{
    \begin{tikzpicture}[overlay, black, every node/.style={draw=none}]
        \node[align=right, inner sep = 0pt] (pagenumber)
            [anchor=south west] at (4ex, 0)
            {\thepage};
    \end{tikzpicture}
}
\fancyhead[LE]{
    \begin{tikzpicture}[overlay, black, every node/.style={draw=none}]
        \node[align=left, inner sep = 0pt] (pagenumber)
            [anchor=south east] at (-4ex, 0)
            {\thepage};
    \end{tikzpicture}
}
\fancyfoot[C]{}

\hangindent=2ex
{
    \Large
    \noindent
    Monsieur \emph{Le Clerc}'s= Character of Mr. \emph{LOCK}'S Method,\par
}
\begin{center}
{W\,I\,T\,H\, H\,I\,S}\\
\vspace{\baselineskip}
{\Huge A\,D\,V\,I\,C\,E}\\
\vspace{\baselineskip}
{About the}\\
\vspace{\baselineskip}
{\Huge U\;S\;E}\\
\vspace{\baselineskip}
{\large O\;F}\\
\vspace{\baselineskip}
{\LARGE Common-Places=.}
\end{center}

\savebox{\dropcap}{\scalefont{2.8}I}
\settoheight{\dropcapheight}{\usebox{\dropcap}}
\settowidth{\dropcapwidth}{\usebox{\dropcap}}
\smash{\raisebox%
    {-\dimexpr \dropcapheight+0.6\thefontsize\relax}%
    {\noindent\usebox{\dropcap}}}%

{\itshape
\setlength{\shapeindent}{\dimexpr \dropcapwidth+1em\relax}
\setlength{\shapelength}{\textwidth}
\addtolength{\shapelength}{-\shapeindent}
\parshape=3
\shapeindent \shapelength
\shapeindent \shapelength
0pt \textwidth
\noindent
N all Sorts= of Learning,
and especially in the Study of Languages=,
the Memory is= the \emph{Treasury or Store-house},
but the Judgment the \emph{Disposer},
which ranges= in Order whatever it hath drawn from the Memory:
But lest the Memory should be Oppressed,
or Over-burthen'd by too many Things=,
Order and Method are to be called in to its= Assistance.
So that when we extract any Thing out of an Author which is= like to be of future Use,
we may be able to find it without any Trouble.
For it would be to little Purpose to spend our Time in Reading of Books=,
if we could not apply what we read to our Use.
It would be just for all the World at serviceable as= a great deal of \emph{Houshold-Stuff},
when if we wanted any particular Thing we could not tell where to find it.
\footnote{Columella out of Cicero, L. 12. Cap. 11.}%
\emph{It is= an Old Saying,
    That that is= the Truest Poverty,
    when if you have Occasion for any Thing,
    you can't use it,
    because you know not where 'tis= laid.}
Many have Wrote much en this= Subject,
and I have made Trial of them,
but I have never met with a better and more easie Method,
than that which I receiv'd from a \footnote{He speaks= of this= Method of Mr. Lock's=.} Friend,
and publish'd in French some Time since.

And I have found, upon several Years= Experience,
this= Method, which is= very well adapted,
not only to the Latin, but also to the Greek Tongue,
to be extraordinary useful.
Neither do I ever look, upon my Latin or Greek Collections=,
but I call to mind the Kindness= of that Excellent and Learned Person,
who taught me that Method.

At the Entrance indeed upon any Study,
when the Judgment is= not sufficiently confirm'd,
nor the Stock of Knowledge over large,
so that the Student are not very well acquainted with what is= worth Collecting,
scarce any Thing is= Extracted,
but what will be useful but for a little while;
because as= the judgment grows= Ripe,
those Things= are despis='d which before were had in esteem.
Yet it is= of Service to have Collections= of this= Kind,
both that Students= may learn the Art of putting Things= in Order,
as= also the better retain what they Read.

But here are Two Things= carefully to be observed;
the First is=, that we extract only those Things= which are Choice and Excellent,
either for the Matter it self,
or else for the Elegancy of the Expression,
and not what comes= next;
for that Labour would abate our Desire to go on with our Reading;
neither are we to think that all those things= are to be writ out which are called
$\Gamma\nu\omega\mu\alpha\iota$, or Sentences=.
Those Things= alone are to be picked out,
which we cannot so readily call to mind,
or for which we should want proper Words= and Expressions=.

For Instance, although the Story in that Place of Virgil where these Words= are,

\emph{Discite Justitiam moniti, \& non temnere Divos=.}

\emph{Being warn'd, \emph{by all these Things=},
learn to do that which is= Just, and
not to despise the Gods=,}

is= worth taking Notice of,
yet I would not have you Write these Words= down,
because there is= Nothing in the Thing it self,
or in the Manner of Expression,
that is= above the Reach of any Ordinary Capacity.

The Second Thing which I would have taken Notice of, is=,
that you don't Write out too much,
but only what is= most Worthy of Observation,
and to mark the Place of the Author from whence you Extract it,
for otherwise it will cause the Loss= of too much Time.

Neither ought any Thing to be Collected whilst you are busied in Reading;
if by taking the Pen in Hand the Thread of your Reading be broken off,
for that will make the Reading both Tedious= and Unpleasant.

The Places= we design to extract from are to be marked upon a piece of Paper,
that we may do it after we have read the Book out;
neither is= it to be done just after the First Reading over of the Book,
but when we have read it a second time.

These Things= it's= likely may seem Minute and Trivial,
but without 'em great Things= cannot subsist;
and these being neglected cause very great Confusion both of Memory and Judgment,
and that which above all Things= is= most to be valued,
Loss= of Time.

Some who otherwise were Men of most extraordinary Parts=,
by the Neglect of these things= have committed great Errors=,
which if they had been so happy as= to have avoided,
they would have been much more serviceable to the Learned World,
and so consequently to Mankind.

And in good Truth,
They who despise such Things=,
do it not so much from any greater share of Wit that they have than their Neighbours=,
as= from Want of Judgment;
whence it is= that they do not well understand how Useful Things= Order and Method are.
}
